% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{enumitem}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-20pt}
\begin{document} 

\name{Ronny Brzezinski\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name
\address{\bf  1029 W Irving Park Rd \\Chicago, IL 60613 \\(857) 407-8840 \\ ronbrz@protonmail.ch}
\begin{resume}
\section{EXPERIENCE}
\vspace{0in}
\begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Software Developer} \>Percipia     \> Feb 2018 - Sept 2018\\
  \>Chicago, IL
\end{tabbing}
\begin{itemize}[leftmargin= .1in] \itemsep -2pt
\item Technical lead and developer for company website, percipia.com. Worked closely
  with designer to bring artistic vision to reality using HTML, Sass, and Go.
\item Built integrations for various third party services for our in room Android application in Java.
\item Extend and upkeep our custom CMS solution written in PHP. Added several features, including
  the ability for hotels to manage their restaurant offerings, and adding functionality allowing guests to
  more easily order food to their room.
\item System administration duties, from ensuring our sites are running correctly to helping our clients
  with issues they may be having with their Asterisk VOIP phone system.
\end{itemize}
\vspace{-.2in}
\begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Back End Web Developer Co-op} \>Clypd     \> Jan 2016 - June 2016\\
  \>Somerville, MA
\end{tabbing}
\begin{itemize}[leftmargin= .1in] \itemsep -2pt
\item Feature lead on project tasked with writing a tool to run workers. Responsibilities
  included writing, scheduling, troubleshooting, and resolving tickets to facilitate project
  implementation.
\item Built features for the Clypd website using Go and SQL. These features include
  authorization middleware, new endpoints, and workers to help gather or synchronize data
  regularly.
\item Collaborated using an Agile workflow, ensuring communication and productivity
\item Utilized Git and Github alongside code reviews to ensure high quality code merges with
  master branch.
\end{itemize}
\vspace{-.2in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer Co-op} \>Novartis \> Jan 2013 - June 2013\\
    \>Cambridge, MA
   \end{tabbing}%\vspace{-10pt}
   \begin{itemize}[leftmargin= .1in] \itemsep -2pt
   \item Created and oversaw running Python script to migrate scientific data from excel files
     to database.
   \item Implemented features and fixed bugs on Novartis intranet website using jQuery.
   \end{itemize}
\vspace{-.2in}
\section{Computer Skills}
Languages:  Python, JavaScript, Java, Go, SQL, and Haskell \\
Software: Git, Emacs, Linux  \\
Other Technologies:  HTML, CSS,  SASS
\section{Personal projects}
        \centerline{https://github.com/ronbrz}\vspace{-.1in} 
        {\bf SMS Get Directions service} Weekend project that allows user to text an address
        and recieve directions. Developed service using Haskell. The use case for this project
        was based on users who are able to text but not access the internet on their device. \\

        \section{VOLUNTEER WORK}
\vspace{-0.1in}
\begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill
  FreeGeekChicago \>\> Aug 2015 - Dec 2015
\end{tabbing}
\begin{itemize}[leftmargin= .1in] \itemsep -2pt
\item Tore down donated computers for viable parts.
\item Built computers using donated parts.
  \item Installed Linux on thes computers, providing a way for people to be able to buy a very inexpensive functional computer.
\end{itemize}
        \section{EDUCATION}
Northeastern University, Boston, MA \\
Candidate for Bachelor of Science, Computer Science   \\

\end{resume}
\end{document}
